Constructive Solid Geometry for Interactive Environments

### 2018-04-26 Paper.tex
Update paper with new random functions

In the idle loop of the game, the position values of the spaceship are changed. If one of the directional booleans is true, \texttt{xpos} or \texttt{ypos} is changed accordingly. When the scene is redrawn, the camera position uses \texttt{xpos} and \texttt{ypos} to remain behind the ship. Another variable, \texttt{zpos} is also changed; this variable does not translate the spaceship itself, but instead translates all other obstacles onscreen. The \texttt{zpos} variable is cyclical; once the value is less than -100, \texttt{zpos} is reset to 0, and the \texttt{speed}, \texttt{zpos}'s rate of change, is increased.\\

@@

Three random floating-point variables between 0 and 1 are created on each cycle; these three variables determine the rotation and position of each obstacle onscreen. For the \texttt{glTranslate} calls, the random numbers are multiplied by 20 then subtracted by 10 to place it within the playing area; the \texttt{glRotate} calls use the random values as they are. Each of the three variables is shuffled in their usage in the objects, so that no object has the same rotation or position as another.
\section{Conclusion}
As a whole, the field of constructive solid geometry poses a number of difficult problems for computer scientists. With real-time rendering infeasible, and the alternative algorithms only suitable in a handful of cases, there is still much research to be done. However, the existing solutions are more than adequate to produce usable and complete software, as evidenced by the display program and the asteroid game.
\newpage
\end{doublespace}
\begin{onehalfspace}
\section{Source Code}
\subsection{OpenSCAD}
\subsubsection{die.scad}
% \lstinputlisting[language=scad]{die.scad}
\subsubsection{connector.scad}
%\lstinputlisting[language=scad]{connector.scad}
\subsubsection{torus.scad}
\lstinputlisting[language=scad]{torus.scad}
\subsubsection{asteroid.scad}
\lstinputlisting[language=scad]{asteroid.scad}
\subsubsection{pipes.scad}
\lstinputlisting[language=scad]{pipes.scad}
\subsubsection{spaceship.scad}
\lstinputlisting[language=scad]{spaceship.scad}
\subsubsection{cookie\_cutter.scad}
\lstinputlisting[language=scad]{cookie_cutter.scad}

>>>>

In the idle loop of the game, the position values of the spaceship are changed. If one of the directional booleans is true, \texttt{xpos} or \texttt{ypos} is changed accordingly. When the scene is redrawn, the camera position uses \texttt{xpos} and \texttt{ypos} to remain behind the ship. Another variable, \texttt{zpos} is also changed; this variable does not translate the spaceship itself, but instead translates all other obstacles onscreen. The \texttt{zpos} variable is cyclical; once the value is less than -100, \texttt{zpos} is reset to The ``playing area'' of the game ends when \texttt{zpos=-100}, at which point it resets to \texttt{zpos = 50*speed+25}, and the \texttt{speed}, \texttt{zpos}'s rate of change, is increased by 0.2 to a max speed of 1.\\

@@

Another struct, \texttt{GameObject}s, is used to hold two three-element arrays; these three variables determine the rotation and position of each obstacle onscreen. A vector of these \texttt{GameObject}s is created in the \texttt{init} function and populated with 7 asteroids. In a for loop, each obstacle in the vector is drawn with its corresponding rotation and position. For the \texttt{glTranslate} calls, the following equation is used to center the asteroids in the xy-plane of the game screen: \texttt{30*obstacles[i].position[0]-15} for x and \texttt{30*obstacles[i].position[1]-15}for y. The bounds on the spaceship are between -10 and 10 on both the x- and y-axis, and this formula bounds the position of the asteroid between -15 and 15. The z-position of the asteroid is determined by \texttt{-90*obstacles[i].position[2]-zpos}.  \\

The \texttt{glRotate} calls use the random values with the equation \texttt{2*obstacles[i].rotation[0]-1} for x, \texttt{2*obstacles[i].rotation[1]-1}, for y, and \texttt{2*obstacles[i].rotation[2]-1} for the z-value of the rotation vector. The angle of rotation is calculated by \texttt{-1.5*zpos}, causing the asteroid to continually rotate as it moves through the scene. By multiplying by 2 and subtracting 1, each component of the rotation vector is bounded between -1 and 1.
\section{Conclusion}
As a whole, the field of constructive solid geometry poses a number of difficult problems for computer scientists. With real-time rendering infeasible, and the alternative algorithms only suitable in a handful of cases, there is still much research to be done. However, the existing solutions are more than adequate to produce usable and complete software, as evidenced by the display program and the asteroid game.
\newpage
\end{doublespace}
\begin{onehalfspace}
\section{Source Code}
\subsection{OpenSCAD}
\subsubsection{die.scad}
% \lstinputlisting[language=scad]{die.scad}
\subsubsection{connector.scad}
%\lstinputlisting[language=scad]{connector.scad}
\subsubsection{torus.scad}
\lstinputlisting[language=scad]{torus.scad}
\subsubsection{asteroid.scad}
\lstinputlisting[language=scad]{asteroid.scad}
\subsubsection{pipes.scad}
\lstinputlisting[language=scad]{pipes.scad}
\subsubsection{spaceship.scad}
\lstinputlisting[language=scad]{spaceship.scad}
\subsubsection{cookie\_cutter.scad}
\lstinputlisting[language=scad]{cookie_cutter.scad}
